Distance/time to travel calculations for hospitals in Scotland

### 2021-08-23 distance_to_nearest_hospital.Rmd
Tried to test if a different list of acute hospitals from another PHS report on quarterly hospital activity would produce different list  of hospitals... but the data ren't given on hospital level, so I can't produce a list of hospitals from those! Also recorded a caveat about the appropriateness of the 'acute hospital' definition

library(tidyverse)  # for tidy workflow
library(readxl)  # for reading excel files
library(tictoc)  # for measuring time taken for calculations
```

@@

```{r}
isds1 <- read_csv("./distance_to_hospital/beds_by_nhs_board_of_treatment_and_specialty.csv", guess=1e5)

acute_hospitals <- hospitals %>% semi_join(isds1, by = "Location")  # keep only hospitals present in the isd(s)1 dataset
```

@@

>>>>

library(tidyverse)  # for tidy workflow
library(readxl)  # for reading excel files
library(tictoc)  # for measuring time taken for calculations

# TODO: work out if OSRM would work...
# library(osrm)  # for OSM routing data
```

@@

@@

Note: when I spoke to Kirsty Anderson (PHS analyst) on 19 August 2021, she suggestd I extract the list of acute hospitals from the Inpatient activity file of the report, so I will check that also. [The report is available here](https://publichealthscotland.scot/media/7504/inpatient-and-daycase-stays-by-nhs-board-of-residence-to-december-2019.csv)
However, these data aren't provided on hospital-level, but on health-board level instead, so a list of hospitals canot be obtained this way!

**Important: Kirsty Anderson of PHS said that the definition of 'acute' is not a singular definition used across the NHS. 'Acute' was defined for the purposes of their reporting hospital activity, and may not be appropriate in other contexts!**

```{r}
isds1_beds <- read_csv("./distance_to_hospital/beds_by_nhs_board_of_treatment_and_specialty.csv", guess=1e5)

acute_hospitals <- hospitals %>% semi_join(isds1_beds, by = "Location")  # keep only hospitals present in the isd(s)1 dataset

# isds1_inpatients <- read_csv("./distance_to_hospital/inpatient-and-daycase-stays-by-nhs-board-of-residence-to-december-2019.csv", guess=1e5)  # note: this doesn't include per-hospital data
```
